Hot and fresh: Pervasive climate stressors of seagrass in a large Gulf coast estuary

### 2023-08-23 manu-draft.qmd
adding mixeff model figure example

@@

>>>>

An example of mixed effects models for two selected thresholds is shown in @fig-mixeff.

@@

![Example of mixed effects models for the estimated number of days by year that salinity (blue) or temperature (red) were below or above thresholds of 25 psu and 30 degrees C, respectively.  The bottom row (black) shows the number of days when both salinity and temperature were below or above the thresholds.  The models included station as a random effect for each bay segment, with grey lines indicating individual station trends and thicker lines indicating the overall model fit.  Slopes for significant models are shown in the bottom right of each facet. OTB: Old Tampa Bay, HB: Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay.](figs/mixeff.png){#fig-mixeff}
